\documentclass[9pt]{article}

\usepackage[T1]{fontenc}
\usepackage{inter} % https://tug.org/FontCatalogue/
\renewcommand*\familydefault{\sfdefault}

\usepackage{geometry}
\geometry{
a4paper,
top=0.5in,
bottom=0.5in,
left=0.5in,
right=0.5in
}

\setcounter{secnumdepth}{0} % remove section numbering
\pdfgentounicode=1 % make ATS friendly

\usepackage{enumitem}
\setlist[itemize]{
    noitemsep,
    left=0pt..1.5em
}
\setlist[description]{itemsep=0pt}
\setlist[enumerate]{align=left, noitemsep}

\usepackage[dvipsnames]{xcolor}
% \usepackage[dvipsnames, svgnames, x11names]{xcolor} 
% \usepackage[dvipsnames]{xcolor} % xcolor.pdf Sec.4 Colors by Name
\colorlet{icnclr}{gray}
% \colorlet [⟨type⟩]{⟨name⟩}[⟨num model⟩]{⟨color ⟩}
% \definecolor[⟨type⟩]{⟨name⟩}{⟨model-list⟩}{⟨spec-list⟩}


\usepackage{titlesec}
% \titlespacing{command}{left spacing}{before spacing}{after spacing}[right]
% \titlespacing{\section}{0pt}{*3}{*1}
\titlespacing{\subsection}{0pt}{*0}{*0}
\titlespacing{\subsubsection}{0pt}{*0}{*0}
% \titleformat{<command>}[<shape>]{<format>}{<label>}{<sec>}{<before-code>}[<after-code>]  
\titleformat{\section}{\color{Sepia}\large\fontseries{black}\selectfont\uppercase}{}{}{\ruleafter}[\global\RemVStrue]
\titleformat{\subsection}{\large\fontseries{semibold}\selectfont}{}{}{\rvs}
\titleformat{\subsubsection}{\large\fontseries{medium}\selectfont}{}{}{}

\usepackage{xhfill} 
\newcommand\ruleafter[1]{#1~\xrfill[.5ex]{1pt}[gray]} % add rule after title in .5 x-height 

\newif\ifRemVS % remove vspace between \section & \subsection
\newcommand{\rvs}{
    \ifRemVS
        \vspace{-1.5ex}
    \fi
    \global\RemVSfalse
}


\usepackage{fontawesome5}

\usepackage[bookmarks=false]{hyperref} % [imp!]
\hypersetup{ 
    colorlinks=true,
    urlcolor=Sepia,
    pdftitle={Kevin Groce Resume},
}

\usepackage[page]{totalcount}
\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}	
\fancyhf{}							
\cfoot{\color{darkgray} Kevin Groce's Resume -- Page \thepage{} of \totalpages}


\begin{document}

%== HEADER ==%
\begin{center}
    {\fontsize{30}{30}\selectfont\interthin KEVIN\interheavy GROCE} \\ \bigskip
    {\color{icnclr}\faEnvelope[regular]} \href{mailto:kev.groce@gmail.com}{kev.groce@gmail.com} 
    $|$ 
    {\color{icnclr}\faIcon{mobile-alt}} \href{tel:5014580233}{(501)458-0233}
    $|$ 
    {\color{icnclr}\faLinkedinIn} \href{https://www.linkedin.com/in/kevin-groce-b90818229/}{linkedin.com/kevin-groce} 
    $|$ 
    {\color{icnclr}\faGithub} \href{https://github.com/kjgthecoder}{kjgthecoder}
\end{center}

\section{Experience}
%===================
\subsection{Gainwell Technologies LLC \hfill Aug 2023 -- Present}
\subsubsection{Associate Professional Programmer Analyst \hfill Conway, AR}
\begin{itemize}
    \item Code, test, debug, and document programs; modify products/systems as needed, in UNIX environment in C. 
    \item Perform data analysis for project support.
    \item Prepare test data and run tests to evaluate unit testing results; develop test plans.
\end{itemize}

\subsection{Gainwell Technologies LLC \hfill [May 2022 - Aug 2022, May 2023 - Aug 2023]}
\subsubsection{C\# .NET Developer - Intern \hfill Conway, AR} 
\begin{itemize}
    \item Participated in and developed a deeper understanding of agile methodologies, specifically working on both scrum and Kanban teams.
    \item Worked with the non-relational document database, MongoDB, and acquired a knowledge of event sourcing patterns and database architecture.
    \item Involved in designing, developing, and debugging Prior Authorization, Drug Rebate, and Provider Management modules using ASP.NET and C\#.
\end{itemize}

\subsection{Acxiom \hfill Nov 2022 - May 2023}
\subsubsection{Delivery Analyst - Intern \hfill Conway, AR}
\begin{itemize}
    \item Delivered data, data products, and information that supported Acxiom’s Partner Product offerings.
    \item Ensured that partners and clients received clean, enhanced, segmented, ready-to-use data. 
    \item Analyzed process and data to ensure efficient delivery of services to Acxiom partners and clients.
\end{itemize}

\subsection{US Air Force Reserves \hfill July 2016 - July 2024}
\subsubsection{Aircraft Electrical and Environmental Systems Mechanic \hfill Barksdale, AFB, LA}
\begin{itemize}
    \item Responsible for the installation, removal, and repair of all electrical and environmental components of the B-52 aircraft.
    \item Follow government mandated technical orders to provide maintenance and troubleshooting. 
    \item Conduct scheduled and unscheduled maintenance and inspections electrical and environmental systems.
\end{itemize}

\section{Projects}
%==================
\subsection{\href{https://github.com/kjgthecoder/bashCopier}{Bash Copier}}
\begin{itemize}
    \item Developed a Python-based GUI application with Tkinter to simplify copying scripts from PDFs to terminals for a Linux/Unix course, incorporating features to maintain formatting and remove line numbers, enhancing Python programming and GUI design skills.
\end{itemize}

\subsection{\href{https://snowball-debt-calculator.click/}{Snowball Debt Calculator}}
\begin{itemize}
    \item Created a web application using Spring Boot and AWS to apply the snowball method for debt repayment planning, demonstrating advanced knowledge in object-oriented programming, cloud services, and application deployment.
\end{itemize}

\subsection{\href{https://github.com/kjgthecoder/RecipeReplay}{Recipe Replay}}
\begin{itemize}
    \item Developed RecipeReplay, a web automation tool using Playwright, MoviePy, Requests, and OpenAI's API to convert cooking videos into formatted written recipes, streamlining the learning process for home cooks.
\end{itemize}

\section{Education}
%===================
\subsection{University of Central Arkansas \hfill May 2023}
\begin{tabular}{@{}p{\textwidth}@{}}
    \textit{BS in Information Systems, Minor in Computer Science} \\
    \vspace{0.0em} % Adjust the space between lines
    \textit{BBA in Marketing, Minor in Spanish} \\
    \vspace{0.0em} % Adjust the space between lines
\end{tabular}

\section{Skills}
%===============
\begin{description}
    \item[Programming Languages] Python, C++, Javascript, C\#, Java, C,  
    \item[Cloud Technologies] AWS: S3, EC2, CloudFront, CloudWatch, Lambda, Glue, ECR, EKS
    \item[Frameworks] React.js, Node.js, Flask, Tkinter, Spring Boot
\end{description}

\end{document}
